---
title: "DREAM follow up analysis"
output: html_notebook
---

This is an analysis of social cogniton data collected as part of a follow up with a subset of patients from the DREAM study. 


```{r warning=FALSE}
library(reshape2)
library(ggplot2)
library(psych)
library(ggExtra)
library(ggpubr)
library(cowplot) 
library(lme4) # Fixed
library(lmerTest) # Mixed modeles
library(car) # Anova
library(data.table)

```

```{r}



# Install dependencies ----
rm(list= ls()) # clear screen
options(scipen=999) # gets rid of scientific notation


#### dataframes ----
df<- read.csv('~/Dropbox/TBI Team Folder/TBI_Apathy/apathyDAT/SOC_DATABASE.csv')

table(df$Group) # Display number of controls and patients
describeBy(df$Age, df$Group)

```

```{r, Formating options}

if (!require("RColorBrewer")) {
install.packages("RColorBrewer")
library(RColorBrewer)
}

library("ggsci")

## Formating options ##
# show_col(pal_npg("nrc")(10))
myPalette <- c("#3399FF","#FF0000")
fillPalette <- (scale_fill_npg()) # (scale_fill_rickandmorty())
colPalette <- (scale_color_npg()) # (scale_color_rickandmorty())
npgGroupPalette <- c("#4DBBD5FF","#E64B35FF")
npgAgentPalette <- c("#00A087FF","#3C5488FF")

# Other colour options
# scale_color_tron() # Good with dark theme

# The errorbars overlapped, so use position_dodge to move them horizontally
pd <- position_dodge(0.1) # move them .05 to the left and right 
ebSize <- 1
pointSize <- 4

# Font type & size
textOption <- element_text(family="Times", size = 22)

```

# Summary table for behavioural measures 
```{r}

# Neuropysch summary table for social cognition paper
#### Loop for extracting values for p-adjustment ####

# Create a character vector of the variables of interest
measure <- c('MPI_abilitySubscale', 'MPI_adjustmentSubscale', 'MPI_participationSubscale', 'MPI_total', 'BDI', 'VAS', 'api_emotional', 'api_social', 'api_behavioural', 'numHighContactRoles', 'numPeople', 'embeddedNetworks', 'TOMMS', 'SF36_generalHealth', 'SF36_physicalFunctioning',  'SF36_emotionalWellbeing', 'SF36_socialFunctioning', 'SF36_pain', 'SF36_energyFatigue')


# doesnt allow passing strings as variables, so this function deals with that
str_eval=function(x) {return(eval(parse(text=x)))}
pval <- c()
W <- c()

# Loop for extracting values
for (value in measure) {
  tmp <- 'df$'
  result <- paste(tmp,value, sep="")
  stat <- wilcox.test(str_eval(result) ~ Group, data=df)$statistic
  p <- wilcox.test(str_eval(result) ~ Group, data=df)$p.value
  pval <- append(pval, p)
  W <- append(W, stat)
}

pAdj <- p.adjust(pval, method = "fdr", n = length(pval))
stat.data <- data.frame(measure, W, pval, pAdj)

```

```{r}

# doesnt allow passing strings as variables, so this function deals with that
str_eval=function(x) {return(eval(parse(text=x)))}
con_mean <- c()
con_std <- c()
pat_mean <- c()
pat_std <- c()

# Loop for extracting values
for (value in measure) {
  tmp <- 'df$'
  result <- paste(tmp,value, sep="")
  
  con_m <- describeBy(str_eval(result),  df$Group)$CON[['mean']]
  con_sd <- describeBy(str_eval(result), df$Group)$CON[['sd']]

  pat_m <- describeBy(str_eval(result), df$Group)$PAT[['mean']]
  pat_sd <- describeBy(str_eval(result), df$Group)$PAT[['sd']]
   
  con_mean <- append(con_mean, con_m)
  con_std <- append(con_std, con_sd)
  pat_mean <- append(pat_mean, pat_m)
  pat_std <- append(pat_std, pat_sd)
}

sum.data <- data.frame(measure, con_mean, con_std, pat_mean, pat_std)


measure =  2.19
nm=((measure - 4)*(-1)) 
nm

```




#### Apathy & Motivation analysis
The distributions for emotional discrimination accuracy appear to seperate between groups however a sifnificant difference is not seen.
No relationship is seen with apathy and emotional recognition. 

# API encoded incorrectly prior to Feb 2019 (this data) - invert scores
```{r}

measure=df$api_total
nm=((measure - 4)*(-1)) # review this https://stackoverflow.com/questions/26877917/reverse-scoring-items
wilcox.test(nm ~ df$Group)

measure=df$api_social
nm=((measure - 4)*(-1)) # review this https://stackoverflow.com/questions/26877917/reverse-scoring-items
wilcox.test(nm ~ df$Group)

# select variables
df.test <- df[c(1, 9, 46:48)]
df.test.m <- melt(df.test, id = c("ID", "Group"))

# Models
# F_model <- lm(value ~ variable + Agent + Group + variable:Agent + variable:Group + Agent:Group, data=df.m)
M_model <- lmer(value ~ variable + Group + variable:Group + (1|ID), data=df.test.m)

#anova(model)
Anova(M_model, type="II")
lsm = lsmeans(M_model, ~Group|variable) 
contrast(lsm, interaction = "pairwise", adjust="tukey")

```
There is a significant difference between groups for total apathy score. Investigating the subscales this is driven by behavior and emotional but is not seen for social. 

# Plotting results for behavioural apathy
```{r}

measure=df$api_behavioural
nm=((measure - 4)*(-1)) # review this https://stackoverflow.com/questions/26877917/reverse-scoring-items

  pmain <- ggplot(df, aes(x = Group, y = nm, color = Group)) +
            geom_jitter(size = pointSize) +
            geom_boxplot(alpha = 0.7) +
            stat_compare_means(label.x = 1.3, label.y = 3.5, size = 6, show.legend = FALSE) +
            scale_colour_manual(values=npgGroupPalette) + 
            ylab("Behavioural Activation") +
            theme(text = element_text(size=24), legend.text = element_text(size = 20))
  
# Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = nm, fill = Group),
                 alpha = 0.7, size = 0.2)+
    coord_flip()+
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) +
    theme(text = element_text(size=18), legend.text = element_text(size = 14))
  
  p2<- insert_yaxis_grob(pmain, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2)  
  
  ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/api_behav.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
    ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/api_behav.png", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)

  
```



# emd total correct
```{r}
# Main plot
  pmain <- ggplot(df, aes(x = Group, y = EM_totalCorrect, color = Group))+
    geom_jitter(size = pointSize, show.legend = F) +
    geom_boxplot(alpha = 0.7, size = 1, show.legend = F) +
    stat_compare_means(label.x = 1.3, size = 6, show.legend = F) +
    ggpubr::color_palette("jco") +
    scale_colour_manual(values=npgGroupPalette) +
    ylab("Total correct") +
    scale_x_discrete(labels=c("PAT" = "Patient", "CON" = "Control")) +
    theme(text = textOption, legend.text = textOption) #element_text(size=20), legend.text = element_text(size = 20

# Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = EM_totalCorrect, fill = Group), alpha = 0.7, size = 0.2)+
    coord_flip()+
    ggpubr::fill_palette("jco") +
    theme(text = textOption, legend.text = textOption) +
    scale_fill_manual(values=npgGroupPalette)

  p2<- insert_yaxis_grob(pmain, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2)

  ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_totalCorrect.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300, useDingbats=FALSE)
    ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_totalCorrect.png", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
```



```{r}
  library(cowplot) 
  # Main plot
  pmain <- ggplot(df, aes(x = BDI, y = EM_totalCorrect, color = Group))+
    geom_point(size = pointSize) +
    geom_smooth(method=lm) +
    ggpubr::color_palette("jco") +
    ylab("Emotional discrimination (total correct)") +
    scale_colour_manual(values=npgGroupPalette) +
    theme(text = textOption, legend.text = textOption)
  
  # Marginal densities along x axis
  xdens <- axis_canvas(pmain, axis = "x") +
    geom_density(data = df, aes(x = BDI, fill = Group), alpha = 0.7, size = 0.2) +
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) +
    theme(text = textOption, legend.text = textOption)    

  # Marginal densities along y axis
  # Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE) +
    geom_density(data = df, aes(x = EM_totalCorrect, fill = Group), alpha = 0.7, size = 0.2 ) +
    coord_flip() +
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) 
  
  p1 <- insert_xaxis_grob(pmain, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2)  
  
  ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/BDI_emd_totalCorrect.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
  
    ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/BDI_emd_totalCorrect.png", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
  
## Stats
cor.test(df$BDI, df$EM_totalCorrect)

## Mixed effect model
# select variables
em.mod <- df[c(1, 9, 75, 44)]

# Rearrange data
em.mod.m <- melt(em.mod, id = c("ID", "Group"))
# Models
M_model <- lmer(value ~ variable + Group + Group:variable + (1|ID), data=em.mod.m)
#anova(model)
Anova(M_model, type="III")


## Correlation per group
# require(plyr)
# func <- function(xx) {
#   return(data.frame(COR = cor(xx$EM_totalCorrect, xx$BDI)))
# }
# xx <- df
# ddply(xx, .(Group), func)

```

EM discrim & network
```{r}

  library(cowplot) 
  # Main plot
  pmain <- ggplot(df, aes(x = numPeople, y = EM_totalCorrect, color = Group)) +
    geom_point(size = pointSize) + 
    geom_smooth(method=lm) + 
    xlim(0,50) +
    ggpubr::color_palette("jco") +
    scale_colour_manual(values=npgGroupPalette) +
    xlab("Number of close contacts") +
    ylab("Total correct") +
    theme(text = textOption, legend.text = textOption)
  
  # Marginal densities along x axis
  xdens <- axis_canvas(pmain, axis = "x") +
    geom_density(data = df, aes(x = numPeople, fill = Group), alpha = 0.7, size = 0.2) +
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) +
    theme(text = textOption, legend.text = textOption)
  
  # Marginal densities along y axis
  # Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = EM_totalCorrect, fill = Group),
                 alpha = 0.7, size = 0.2)+
    coord_flip()+
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) 
  
  p1 <- insert_xaxis_grob(pmain, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2)  
  
  ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/EM_totalCorrect_network.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
  
    ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/EM_totalCorrect_network.png", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
  
  cor.test(df$EM_totalCorrect, df$numPeople, method="spearman")
  describeBy(df$numPeople, df$Group)
  wilcox.test(df$numPeople ~ df$Group) 
  
  
## Mixed effect model
# select variables
em.mod <- df[c(1, 9, 75, 50)]

# Rearrange data
em.mod.m <- melt(em.mod, id = c("ID", "Group"))
# Models
M_model <- lmer(value ~ Group*variable + (1|ID), data=em.mod.m)
Anova(M_model, type="II")
lsm = lsmeans(M_model, ~Group)
contrast(lsm, interaction = "pairwise", adjust="tukey")



# # Models
# M_model <- lm(EM_totalCorrect ~ numPeople*Group, data=df)
# Anova(M_model, type="II")
# lsm = lsmeans(M_model, ~Group)
# contrast(lsm, interaction = "pairwise", adjust="tukey")
# 
# df2 <- df[which(df$Group=="PAT"),]
# cor.test(df2$EM_totalCorrect, df2$numPeople, method="spearman")

```


# BDI & Social network size
```{r}

  library(cowplot) 
  # Main plot
  pmain <- ggplot(df, aes(x = BDI, y = numPeople, color = Group)) +
    geom_point(size = pointSize) + 
    geom_smooth(method=lm) + 
    ylim(0,50) +
    ggpubr::color_palette("jco") +
    scale_colour_manual(values=npgGroupPalette) +
    ylab("Number of people") +
    theme(text = textOption, legend.text = textOption)
  
  # Marginal densities along x axis
  xdens <- axis_canvas(pmain, axis = "x") +
    geom_density(data = df, aes(x = BDI, fill = Group), alpha = 0.7, size = 0.2) +
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) +
    theme(text = textOption, legend.text = textOption)
  
  # Marginal densities along y axis
  # Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = numPeople, fill = Group),
                 alpha = 0.7, size = 0.2)+
    coord_flip()+
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette) 
  
  p1 <- insert_xaxis_grob(pmain, xdens, grid::unit(.2, "null"), position = "top")
  p2<- insert_yaxis_grob(p1, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2)  
  
  ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/BDI_network.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
  
    ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/BDI_network.png", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
  
    cor.test(df$BDI, df$numPeople)
  describeBy(df$numPeople, df$Group)
  wilcox.test(df$numPeople ~ df$Group) 
  
  
## Mixed effect model
# select variables
em.mod <- df[c(1, 9, 75, 50)]

# Rearrange data
em.mod.m <- melt(em.mod, id = c("ID", "Group"))
# Models
M_model <- lmer(value ~ variable + Group + Group:variable + (1|ID), data=em.mod.m)
#anova(model)
Anova(M_model, type="II")


```






## Emotional Discrimination RT
```{r}
#Emotional Discrimination RT
    names(df)
    
    # Calculate the cost between congruent and incongruent
    df$costRT <- (df$EM_InCongRT - df$EM_CongRT)
    cost_percent <- (df$EM_InCongRT - df$EM_CongRT)/(df$EM_CongRT) # scales it 
    
    # t-test against 0
    #plot(df$costRT)
    t.test(df$costRT)
    describeBy(df$costRT, df$Group)
    #plot(cost_percent)
    t.test(cost_percent)
    
# Checking assumptions of normality 
  qplot(data = df, x = costRT) + ylab("InCong-Cong RT cost") 
  
# install.packages('data.table') may need to be run if you don't have the
# package
# library(data.table)
outlierReplace = function(dataframe, cols, rows, newValue = NA) {
    if (any(rows)) {
        set(dataframe, rows, cols, newValue)
    }
}

outlierReplace(df, "costRT", which(df$costRT < -100), NA)

#qplot(data = df, x = costRT) + ylab("InCong-Cong RT cost")

wilcox.test(df$costRT ~ df$Group)

#library(cowplot) 
# Main plot
  pmain <- ggplot(df, aes(x = Group, y = costRT, colour=df$Group)) +
              geom_jitter(size = pointSize, show.legend = F) +
              geom_boxplot(alpha = 0.5, outlier.shape = NA, show.legend = F) +
              stat_compare_means(label.x = 1.3, size = 6, show.legend = F) +
              ggpubr::color_palette("jco") +
              scale_colour_manual(values=npgGroupPalette) +
              labs(y = "RT cost (ms)", colour = "Group") +
              scale_x_discrete(labels=c("PAT" = "Patient", "CON" = "Control")) +
              theme(text = textOption, legend.text = textOption)
      
  
  # Marginal densities along y axis
  # Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE) +
            geom_density(data = df, aes(x = costRT, fill = Group), alpha = 0.7, size = 0.2) +
            coord_flip() +
            ggpubr::fill_palette("jco") +
            scale_fill_manual(values=npgGroupPalette) 

  p2<- insert_yaxis_grob(pmain, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2) 
  
 ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_costRT.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
 ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_costRT.png", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)

```






```{r}


  # Calculate the cost between congruent and incongruent accuracy  
  cost <- (df$EM_inCongAcc - df$EM_congAcc) 
  cost_percent <- (df$EM_inCongAcc - df$EM_congAcc)/(df$EM_congAcc) # scales it

  plot(cost) 
  t.test(cost)

  plot(cost_percent) 
  t.test(cost_percent)
  describeBy(cost)
  wilcox.test(cost_percent ~ df$Group)

  library(cowplot) # Main plot 
  pmain <- ggplot(df, aes(x = Group, y = cost_percent, colour=df$Group)) +
    geom_jitter(size = pointSize) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) + 
    ggpubr::color_palette("jco") +
    stat_compare_means(label.x = 1.3, size = 6) +
    scale_colour_manual(values=npgGroupPalette) +
    labs( y = "Accuracy cost", colour = "Group") +
    theme(text = textOption, legend.text = textOption)


  # Marginal densities along y axis # Need to set coord_flip = TRUE, if you plan to use coord_flip() 
  
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE) + 
    geom_density(data = df, aes(x = cost_percent, fill = Group), alpha = 0.7, size = 0.2) + 
    coord_flip() + 
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette)

  p2<- insert_yaxis_grob(pmain, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p2)

ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_costAcc.pdf", plot = p2, width = 12, height = 8, units = c("in"), dpi = 300)
```

p-value = 0.04643 rounded to 3 decimal places is 0.05 which is to be rejected. 

# Same as above with DeHa removed 0.33
```{r}

# Calculate the cost between congruent and incongruent accuracy 
df$Acc_cost <- (df$EM_inCongAcc - df$EM_congAcc)
cost_percent <- (df$EM_inCongAcc - df$EM_congAcc)/(df$EM_congAcc) # scales it 

#qplot(data = df, x = cost) + ylab("InCong-Cong accuracy") + 

# install.packages('data.table') may need to be run if you don't have the
# package
# library(data.table)
outlierReplace = function(dataframe, cols, rows, newValue = NA) {
    if (any(rows)) {
        set(dataframe, rows, cols, newValue)
    }
}

outlierReplace(df, "Acc_cost", which(df$Acc_cost > 0.2), NA)
qplot(data = df, x = Acc_cost) + ylab("InCong-Cong accuracy")


  #plot(df$Acc_cost)
  t.test(df$Acc_cost)
  wilcox.test(df$Acc_cost ~ df$Group)

  library(cowplot) 
  # Main plot
  pmain <- ggplot(df, aes(x = Group, y = Acc_cost, colour = Group)) +
    geom_jitter(size = pointSize, show.legend = F) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA, show.legend = F) + 
    ggpubr::color_palette("jco") +
    stat_compare_means(label.x = 1.3, size = 6, show.legend = F) +
    scale_colour_manual(values=npgGroupPalette) +
    labs( y = "Accuracy cost", colour = "Group") +
    scale_x_discrete(labels=c("PAT" = "Patient", "CON" = "Control")) +
    theme(text = textOption, legend.text = textOption)
      
  
  # Marginal densities along y axis
  # Need to set coord_flip = TRUE, if you plan to use coord_flip()
  ydens <- axis_canvas(pmain, axis = "y", coord_flip = TRUE)+
    geom_density(data = df, aes(x = cost_percent, fill = Group), alpha = 0.7, size = 0.2) + 
    coord_flip() + 
    ggpubr::fill_palette("jco") +
    scale_fill_manual(values=npgGroupPalette)

  p3<- insert_yaxis_grob(pmain, ydens, grid::unit(.2, "null"), position = "right")
  ggdraw(p3) 
  
  
ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_costAcc_norm.pdf", plot = p3, width = 12, height = 8, units = c("in"), dpi = 300)
ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_costAcc_norm.png", plot = p3, width = 12, height = 8, units = c("in"), dpi = 300) 
  
  
# fPlot <- ggarrange(
#          p2,
#          p3,
#          nrow = 1, ncol = 2) # ,common.legend = TRUE, legend = "right"
# 
# ggdraw(fPlot)
#   
#     
# ggsave("~/Google Drive/Imperial/PhD/Thesis/Ch6 Emotional processing/rPlots/soc/emd_costAcc_facet.pdf", plot = fPlot, width = 12, height = 8, units = c("in"), dpi = 300)
    
```
After removing an outlier DeHa who had much greater accuracy for incongruent than congruent there is a significant difference between groups for accuracy cost. W = 355, p-value = 0.0422

